Formalizing Stack Safety as a Security Property

### 2023-02-04 submission5/core.tex
Last responses

Therefore, any low-level treatment of stack safety must begin by asking:
which high-level features does our system support, and what are their
security requirements? Different answers will beget different properties.
We identify and define five security requirements that a system might try
to enforce upon a function call: well-bracketed control flow, and the
integrity and confidentiality of each of the caller and the callee.
These are by no means exhaustive. We apply these first to a simple system
with very few features, then to a more realistic one supporting
tailcall-elimination, argument passing on the stack, and callee-saves
registers.

@@

\paragraph*{Security Semantics and Property Structure}
A security semantics extends a machine
with additional context about the identities of current and pending
functions (which act as security principals) and about the registers and memory they require
to be secure. This added context is purely notional;
it does not affect the behavior of the real machine. The security context
evolves dynamically through the execution of security-relevant operations,
which include events like calls, returns, and frame manipulation.
Our security properties are phrased in terms of this context, often as predicates
on future states (``when control returns to the current function...'')
or as relations on traces of future execution
(hyper-properties).\bcp{This is the first we've mentioned
  hyperproperties.  CSF readers may be surprised.}
\sna{Surprised that we have hyperproperties,
  or that we made it this far without mentioning them?}

@@

\sna{See commented out tex for content that could be massaged to fit in here,
  depending on whether we're interested in delving deeper.}
%For instance, the stack-safety specification from Georges et al.
%\cite{Georges22:TempsDesCerises} supposes a machine with only straightforward call-and-return
%control flow, and therefore defines {\em Well-bracketed Control Flow} (\(\wbcf\)) under the assumption that
%a callee should always return to its caller. But, in the presence of tail-call elimination, a
%return from a callee to a distant ancestor is perfectly reasonable. Similarly, the preceding work by
%Skorstengaard et al. \cite{SkorstengaardSTKJFP} made no mention of confidentiality, even though
%their enforcement mechanism did protect the confidentiality of the caller (though not the callee).

>>>>

Therefore, any low-level treatment of stack safety must begin by asking:
which high-level features does our system support, and what are their
security requirements? Different answers will beget different properties.
We identify and define five security requirements that a system might try
to enforce upon a function call: well-bracketed control flow, and the
integrity and confidentiality of each of the caller and the callee.
These are by no means exhaustive\bcp{That comment belongs in the
  future work
  section, not here}. We apply these first to a simple system
with very few features, then to a more realistic one supporting
tailcall-elimination, argument passing on the stack, and callee-saves
registers.

@@

\paragraph*{Security Semantics and Property Structure}
A security semantics extends a machine
with additional context about the identities of current and pending
functions (which act as security principals) and about the registers and memory they require
to be secure. This added context is purely notional;
it does not affect the behavior of the real machine. The security context
evolves dynamically through the execution of security-relevant operations,
which include events like calls, returns, and frame manipulation.
Our security properties are phrased in terms of this context, often as predicates
on future states (``when control returns to the current function...'')
or as relations on traces of future execution
(hyper-properties).\bcp{This is the first we've mentioned
  hyperproperties.  CSF readers may be surprised.}
\sna{Surprised that we have hyperproperties,
  or that we made it this far without mentioning them?}
\bcp{The latter!}

@@

\sna{See commented out tex for content that could be massaged to fit in here,
  depending on whether we're interested in delving deeper.}\bcp{If
  there's space, some of this could be resuscitated in the related
  work section.  But removing it from here is a good call.}
%For instance, the stack-safety specification from Georges et al.
%\cite{Georges22:TempsDesCerises} supposes a machine with only straightforward call-and-return
%control flow, and therefore defines {\em Well-bracketed Control Flow} (\(\wbcf\)) under the assumption that
%a callee should always return to its caller. But, in the presence of tail-call elimination, a
%return from a callee to a distant ancestor is perfectly reasonable. Similarly, the preceding work by
%Skorstengaard et al. \cite{SkorstengaardSTKJFP} made no mention of confidentiality, even though
%their enforcement mechanism did protect the confidentiality of the caller (though not the callee).
